Analyzing differences in satisfaction and dissatisfaction between Chinese and English-speaking customers of Japanese hotels with machine learning

### 2020-09-27 2_revisions/V0_Before submission/V0_4_Third draft/itt-emotion_V0_3.tex
First data commit: V2-1, before second review

\documentclass[review]{elsarticle}

@@

%to have numbered 4th level sections 1.1.1.1
\setcounter{tocdepth}{4}
\setcounter{secnumdepth}{4}

% to remove period in 4th level sections 1.1.1.1
\makeatletter
\def\els@aparagraph[#1]#2{\elsparagraph[#1]{#2}}
\def\els@bparagraph#1{\elsparagraph*{#1}}
\makeatother
% to enter a newline after 4th level sections
\newcommand{\myparagraph}[1]{\paragraph{#1}\mbox{}\smallskip}

@@

\journal{Tourism Management}

%% APA style
\bibliographystyle{model5-names}\biboptions{authoryear}

@@

\begin{frontmatter}

@@

%% or include affiliations in footnotes:
\author[gidai]{Elisa Claire Alemán Carreón
\corref{mycorrespondingauthor}}
\ead{elisa.claire.aleman.carreon@gmail.com}
% \orcid{0000-0002-6437-0866}

\author[gidai]{Hugo Alberto Mendoza Espa\~na}
\ead{s173330@stn.nagaokaut.ac.jp}

\author[gidai]{Hirofumi Nonaka}
\ead{nonaka@kjs.nagaokaut.ac.jp}

\author[nagasaki]{Toru Hiraoka}
\ead{hiraoka@sun.ac.jp}

\address[gidai]{Nagaoka University of Technology, Nagaoka, Japan}
\address[nagasaki]{University of Nagasaki, Nagasaki, Japan}

\cortext[mycorrespondingauthor]{
Corresponding author%: \\
% Elisa Claire Alemán Carreón \\
% Mailing Address: P.C. 940-2033, Ribbon Nagaoka B104, 1128-3 Kaminozoki-machi, Nagaoka, Niigata, Japan \\
% Cell Phone: 080-9869-4756 \\
}

@@

\medskip
\noindent\it{Highlights}
\begin{itemize}
    \item Chinese customers tend to prefer big and clean spaces but are unsatisfied with Chinese-friendliness.
    \item English-speaking customers are satisfied with friendly staff, but dislike rooms that are dirty or smell of cigarette.
    \item Both customer groups value the location of the hotel as a secondary factor for satisfaction.
    \item Both customer groups have concerns about the pricing of hotels (value for money).
    \item Satisfaction and dissatisfaction of customers come from managerial and environmental attributes of the hotel.
\end{itemize}

@@

\begin{keyword}
Sentiment Analysis\sep Hotels and Lodging\sep Machine Learning\sep Chinese\sep English\sep Preferences
\end{keyword}

\end{frontmatter}

@@

\section*{Acknowledgments}

During our research, we received the commentary and discussion necessary to understand certain cultural aspects that could influence the interpretation of the data by our dear colleagues, whom we would like to show gratitude to, Mr. Zhou Liangyuan, Ms. Fan Min and Ms. Eerdengqiqige. We would also like to show gratitude to Ms. Jajus Aleksandra, from whom we also received notes on the editing and commentary on the content of our manuscript.

@@

@@

\section*{References}

>>>>

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended,natbib]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof

\usepackage{scalerel}
\usepackage{tikz}
\usetikzlibrary{svg.path}

\definecolor{orcidlogocol}{HTML}{A6CE39}
\tikzset{
  orcidlogo/.pic={
    \fill[orcidlogocol] svg{M256,128c0,70.7-57.3,128-128,128C57.3,256,0,198.7,0,128C0,57.3,57.3,0,128,0C198.7,0,256,57.3,256,128z};
    \fill[white] svg{M86.3,186.2H70.9V79.1h15.4v48.4V186.2z}
                 svg{M108.9,79.1h41.6c39.6,0,57,28.3,57,53.6c0,27.5-21.5,53.6-56.8,53.6h-41.8V79.1z M124.3,172.4h24.5c34.9,0,42.9-26.5,42.9-39.7c0-21.5-13.7-39.7-43.7-39.7h-23.7V172.4z}
                 svg{M88.7,56.8c0,5.5-4.5,10.1-10.1,10.1c-5.6,0-10.1-4.6-10.1-10.1c0-5.6,4.5-10.1,10.1-10.1C84.2,46.7,88.7,51.3,88.7,56.8z};
  }
}

\newcommand\orcidicon[1]{\href{https://orcid.org/#1}{\mbox{\scalerel*{
\begin{tikzpicture}[yscale=-1,transform shape]
\pic{orcidlogo};
\end{tikzpicture}
}{|}}}}

@@

@@

\usepackage{xcolor}
\newcommand{\orcid}[1]{\href{https://orcid.org/#1}{\textcolor[HTML]{A6CE39}{\aiOrcid}}}

\journalname{Information Technology \& Tourism}

\bibliographystyle{spbasic}
%% APA style
% \bibliographystyle{model5-names}\biboptions{authoryear}

@@

@@

\titlerunning{Differences between Chinese and English-speaking customers of Japanese hotels}

\author{Elisa Claire Alem\'an Carre\'on \orcidicon{0000-0002-6437-0866} \and
        Hugo Alberto Mendoza Espa\~na                                   \and
        Hirofumi Nonaka                                                 \and
        Toru Hiraoka
}

\authorrunning{E. Alemán Carreón et al.}

\institute{Elisa Claire Alem\'an Carre\'on \at
            Nagaoka University of Technology, Nagaoka, Japan \\
            ORCID: 0000-0002-6437-0866 \\
            \email{elisa.claire.aleman.carreon@gmail.com}           %  \\
            % \emph{Present address:P.C. 940-2033, Ribbon Nagaoka B104, 1128-3 Kaminozoki-machi, Nagaoka, Niigata, Japan}
        \and
            Hugo Alberto Mendoza Espa\~na \at
            Nagaoka University of Technology, Nagaoka, Japan \\
            \email{s173330@stn.nagaokaut.ac.jp}
        \and
            Hirofumi Nonaka \at
            Nagaoka University of Technology, Nagaoka, Japan \\
            \email{nonaka@kjs.nagaokaut.ac.jp}
        \and
            Toru Hiraoka \at
            University of Nagasaki, Nagasaki, Japan \\
            \email{hiraoka@sun.ac.jp}
}

% Corresponding author%: \\
% % Elisa Claire Alemán Carreón \\
% % Mailing Address: P.C. 940-2033, Ribbon Nagaoka B104, 1128-3 Kaminozoki-machi, Nagaoka, Niigata, Japan \\
% % Cell Phone: 080-9869-4756 \\
% % ORCID: 0000-0002-6437-0866

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

\maketitle

@@

% \medskip
% \noindent\it{Highlights}
% \begin{itemize}
%     \item Chinese customers tend to prefer big and clean spaces but are unsatisfied with Chinese-friendliness.
%     \item English-speaking customers are satisfied with friendly staff, but dislike rooms that are dirty or smell of cigarette.
%     \item Both customer groups value the location of the hotel as a secondary factor for satisfaction.
%     \item Both customer groups have concerns about the pricing of hotels (value for money).
%     \item Satisfaction and dissatisfaction of customers come from managerial and environmental attributes of the hotel.
% \end{itemize}

\keywords{Sentiment Analysis\and Hotels and Lodging\and Machine Learning\and Chinese\and English\and Preferences}

@@

@@

\begin{acknowledgements}

During our research, we received the commentary and discussion necessary to understand certain cultural aspects that could influence the interpretation of the data by our dear colleagues, whom we would like to show gratitude to, Mr. Liangyuan Zhou, Ms. Min Fan and Ms. Eerdengqiqige. We would also like to show gratitude to Ms. Aleksandra Jajus, from whom we also received notes on the editing and commentary on the content of our manuscript.

@@

\end{acknowledgements}

@@

% \section*{References}
